### 2010-03-23 papers/icfp-2010-desc/paper_idesc.tex
IDesc@ICFP: fix typo in substI
Desc@ICFP: remove \Epolym, instead abstract over the type. pwm: is that presentation more convincing?

%% Types
\newcommand{\Ty}{\C{Ty}}
\newcommand{\Ebool}{\etag{\CN{bool}}}
\newcommand{\Enat}{\etag{\CN{nat}}}
\newcommand{\Epolym}{\etag{\alpha}}

@@

\[
\begin{array}{l@{\::\:\:}l}
\Econd{}{}{}     & \Ebool \To \Epolym \To \Epolym \To \Epolym  \\ 
\Eplus{}{}       & \Enat \To \Enat \To \Enat                   \\
\Ele{}{}         & \Enat \To \Enat \To \Ebool                  \\
\Eval{}          & \Val{\Epolym} \To \Epolym
\end{array}
\]

The notation $\Epolym$ represents a form of ``polymorphism'', meaning
that $\alpha$ can be any type. \note{Polymorph? Will any ghost try to
  haunt me with that?  A ghost under a mixed prefix?
  Aaaaaaaaaaargh\ldots (Wha? - pwm)}
\note{pwm: I don't really get the need for this $\Epolym$ notation. Why not
just abstract over an elem of $\Ty£$?}

The function $\Val{}$, used in the definition of $\Eval{}$, simply
maps $\Epolym$ to the corresponding type in the host language. Hence,
the argument of $\Eval{}$ are ensured to be of the expected type. We
assume $\Nat$ and $\Bool$ represent natural numbers and booleans in
the host language. Further, we also assume the existence of an
addition and comparison operator in $\Nat$, respectively named
$\F{plusHost}$ and $\F{leHost}$. We define $\Val{}$ as follow:

@@

\[
\begin{array}{@{}ll}
\substI : & \PITEL{\V{I}}{\Set}
            \PITEL{\V{X}, \V{Y}}{\V{I} \To \Set}
            \PITEL{\V{R}}{\TagIDesc{\V{I}}} \\
          & \PITEL{\V{\sigma}}{\PI{\V{i}}{\V{I}} \V{X}\:\V{i} \To 
                               \IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{Y}})}{\V{i}}} \\
          & \PITEL{\V{i}}{\V{I}}
            \PITEL{\V{D}}{\IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{X}})}{\V{i}}} \To
            \IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{Y}})}{\V{i}}
\end{array}
\]

>>>>

%% Types
\newcommand{\Ty}{\C{Ty}}
\newcommand{\Ebool}{\etag{\CN{bool}}}
\newcommand{\Enat}{\etag{\CN{nat}}}

@@

\[
\begin{array}{l@{\::\:\:}l}
\Econd{}{}{}     & \forall \Bhab{ty}{\Ty} . \Ebool \To ty \To ty \To ty  \\ 
\Eplus{}{}       & \Enat \To \Enat \To \Enat                           \\
\Ele{}{}         & \Enat \To \Enat \To \Ebool                          \\
\Eval{}          & \forall \Bhab{ty}{\Ty} . \Val{ty} \To ty
\end{array}
\]

The function $\Val{}$, used in the definition of $\Eval{}$, simply
maps an object type $ty$ to the corresponding type in the host
language. Hence, the argument of $\Eval{}$ are ensured to be of the
expected type. We assume $\Nat$ and $\Bool$ represent natural numbers
and booleans in the host language. Further, we also assume the
existence of an addition and comparison operator in $\Nat$,
respectively named $\F{plusHost}$ and $\F{leHost}$. We define $\Val{}$
as follow:

@@

\[
\begin{array}{@{}ll}
\substI : & \PITEL{\V{I}}{\Set}
            \PITEL{\V{X}, \V{Y}}{\V{I} \To \Set}
            \PITEL{\V{R}}{\TagIDesc{\V{I}}} \\
          & \PITEL{\V{\sigma}}{\PI{\V{i}}{\V{I}} \V{X}\:\V{i} \To 
                               \IMu{I}{(\toIDesc{\FreeIMonad{\V{R}}{\V{I}}{\V{Y}}})}{\V{i}}} \\
          & \PITEL{\V{i}}{\V{I}}
            \PITEL{\V{D}}{\IMu{I}{(\toIDesc{\FreeIMonad{\V{R}}{\V{I}}{\V{X}}})}{\V{i}}} \To
            \IMu{I}{(\toIDesc{\FreeIMonad{\V{R}}{\V{I}}{\V{Y}}})}{\V{i}}
\end{array}
\]
